% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      
I want to thank the York Plasma Institute and more widely the Fusion Centre for Doctoral Training for giving me the opportunity to pursue this research. It has been a pleasure to study, learn and then gradually make my own contribution to the field. My supervisors John Pasley, initially Lee Morgan and latterly Michael Fleming have all been generous with their time, giving guidance and reassurance when I needed it. 

Thanks to Jon Shimwell, Andrew Turner, Jon Naish, Bethany Colling, Tim Eade and all the other staff at the Culham Centre for Fusion Energy (CCFE). Their skills, advice, favours, amusing cynicism and questionable softball tactics have made my time at Culham all the more enjoyable. I give my thanks and best wishes to the current and past students of CCFE. Let us pray that if Charlie ever achieves a position of power he exercises it benevolently. I must credit the role that lunchtime football has had in facilitating my otherwise sedentary work. I will miss Darren's bombast, Alan's sarcasm and Jorge's finesse. Long may those games continue. 

Thanks to Igor Lengar of the Jo\v zef Stefan Institute for sharing his radiation transport models with me. I am very appreciative to Michael Loughlin for his advice and for arranging the research placement at ITER Organisation in Provence, it was a privilege. Jakhar Shrichand and Vladimir Barabash of ITER were also a great help to my work.

Outside of professional life, thank you to my girlfriend, Caitlin, for her silly dancing, serious counsel and shared jokes over the past four years. Also, to my parents, Max (who reminds me to work) and Gill (who reminds me there is much else, too). My friends in Oxford have been a persistent and growing joy since not long after I moved here and I credit our community with keeping me calm and content. You're all wonderful.

This work was funded by the Engineering and Physical Sciences Research Council (EPSRC) through grant EP/L01663X/1.
\end{acknowledgements}
